Democracy, Public Support, and Measurement Uncertainty

### 2021-06-01 paper/dcpo_demsupport.Rmd
full result presented; need rerun the uncertains to measure everything works correctly

#saveRDS(result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
```

@@

load(here("output", "estimates_clsMeanAPSR.RDS"))
result_clsUncertainAPSR <- readRDS(here("output", "estimates_clsAPSR.RDS"))
result_dcpoAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))

@@

```{r visualizeFullUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=10}

>>>>

saveRDS(result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
```

@@

result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
load(here("output", "estimates_clsAPSR.RDS"))
result_dcpoAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))

@@

```{r visualizeFullUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=7}
